\begin{thebibliography}{99}
    \bibitem{parker} L.E. Parker, 
    \emph{Distributed Intelligence: Overview of the Field and its
    Application in Multi-Robot Systems}, March 2008.

    \bibitem{maxsum} A. Farinelli, N. Boscolo, E. Zanotto, E. Pagello,
    \emph{Advanced Approaches for Multi-Robot Coordination in
    Logistic Scenarios}, April 2017.

    \bibitem{mapd} H. Ma, W. Hönig, T.K.S. Kumar, N. Ayanian, S. Koenig,
    \emph{Lifelong Path Planning with Kinematic Constraints
    for Multi-Agent Pickup and Delivery}, December 2018.

    \bibitem{cooros} T. Andre, D. Neuhold, C. Bettstetter,
    \emph{Coordinated Multi-Robot Exploration:
    Out of the Box Packages for ROS}, December 2014.

    \bibitem{cf_farinelli} A. Farinelli, M. Bicego, F. Bistaffa, S. D. Ramchurn,
    \emph{A Hierarchical Clustering Approach to Large-scale
    Near-optimal Coalition Formation with Quality
    Guarantees}, March 2017.

    \bibitem{cf_greedy} X. Zheng, S. Koenig,
    \emph{Greedy Approaches for Solving Task-Allocation Problems with Coalitions}
    , 2008.

    \bibitem{partition} M. Orlov,
    \emph{Efficient Generation of Set Partitions}, March 2002.

    \bibitem{farinelli_coo} A. Farinelli, L. Iocchi, D. Nardi,
    \emph{Multirobot Systems: A Classification
    Focused on Coordination}, October 2004.

    \bibitem{market-based} R. Zlot, A. Stentz, 
    \emph{Market-based Multirobot Coordination for Complex Tasks}, January 2006.

    \bibitem{mapf} H. MA, J. Li, T. K. S. Kumar, S. Koenig,
    \emph{Lifelong Multi-Agent Path Finding
    for Online Pickup and Delivery Tasks}, May 2017.

    \bibitem{decoo} R. Stranders, A. Farinelli, A. Rogers, N. R. Jennings,
    \emph{Decentralised Coordination of Mobile Sensors Using the Max-Sum Algorithm}, 2009.

    \bibitem{focoo} A. Farinelli, L. Iocchi, D. Nardi,
    \emph{Multirobot Systems: A Classification
    Focused on Coordination}, October 2004.

    \bibitem{autocoo}, C. Jones, M. J. Mataric,
    \emph{Automatic Synthesis of Communication-Based
    Coordinated Multi-Robot Systems}, October 2004.

    \bibitem{coocoo}, P. R. Wurman, R. D'AndreA, M. Mountz,
    \emph{Coordinating Hundreds of
    Cooperative, Autonomous
    Vehicles in Warehouses}, March 2008.
    
    
\end{thebibliography}